### 2023-12-12 manuscript.tex
remove links, add references until data_and_model_availability [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/f4aeb90fb62535045c66cedb190c0d8e1c3373b7.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/f4aeb90fb62535045c66cedb190c0d8e1c3373b7/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/7182199155

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/2dd6a10f7098d9d0ba158bfa18b15f0c218196e6/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/2dd6a10f7098d9d0ba158bfa18b15f0c218196e6}{MMV-Lab/im2im-paper@2dd6a10}
on December 12, 2023.

@@

Finally, we showed the comparison between three different types of models, an FCN-type model (i.e., fnet), a pix2pix-type model, and a cycleGAN-type model. For fair comparison, we used fnet as the same backbone for all three types of models. In theory, the pix2pix-type model can be trained in two different ways: from scratch or initializing the generator with a pre-trained fnet (trained as FCN). Examples of the comparison results were shown in the last two rows in Figure \ref{fig:labelfree_all_structures}-B. Visually, it is evident that the additional adversarial components (i.e., the discriminator) could generate images with more realistic appearance than a typical FCN-type model alone, but again, we leave the appropriate quantitative evaluations to users' specific biomedical studies.

@@

For 2D demonstration, we extracted the middle Z-slice from NPM1 images as the training target, while using the NPM1 segmentation results as the input binary masks. With the paired ``mask + microscopy image'' data, we could train the model in a supervised fashion, or randomly shuffle the data to simulate the situation without paired data which can be trained in an unsupervised fashion using the cycleGAN-type framework implemented in \emph{MMV\_Im2Im}. Example results can be found in Figure \ref{fig:synthetic}-A and Table \ref{tbl:syn}. In general, the supervised synthesization can generate more realistic images than the unsupervised model.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\caption{Overview of the used frameworks for the demonstrated tasks. \label{tbl:framework_overview}}\label{tbl:framework_overview}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Task
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dim
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Framework
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backbone
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Task
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dim
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Framework
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backbone
\end{minipage} \\
\midrule()
\endhead
Labelfree & 2D/3D & FCN, Pix2pix, cyleGAN & fnet, UNet, AttentionUnet, SwinUNETR, \ldots{} \\
Semantic segmentation & 2D/3D & FCN, cycleGAN & AttentionUnet, DynUnet, UNet3D \\
Instance segmentation & 2D/3D & EmbedSeg & BranchedERFNet\_2d, UNet3D \\
Synthetic & 2D/3D & Pix2pix & AttentionUnet, fnet \\
Denoising & 3D & FCN & UNet \\
Modality transformation & 3D & FCN & UNet3D \\
Staining transformation & 2D & Pix2pix & predefined\_unet \\
\bottomrule()
\end{longtable}

@@

Overall, the package inherited the boilerplate concept from pytorch-lightning (\url{https://www.pytorchlightning.ai/}), and was made fully configurable via yaml files supported by pyrallis (\url{https://github.com/eladrich/pyrallis}), as well as largely employed state-of-the-art DL components from MONAI (\url{https://monai.io/}). The three key parts in the package: \texttt{mmv\_im2im.models}, \texttt{mmv\_im2im.data\_modules}, and \texttt{Trainers}, will be further described below.

@@

In general, there are mainly four major DL frameworks that could be applied to microscopy image-to-image transformation: supervised learning with a fully convolutional networks (FCN) type models, supervised learning with pix2pix type models, unsupervised learning to learn mapping between visual domains, and Self2Self-type self-supervised learning {[}\protect\hyperlink{ref-tuObtXMR}{44}{]}. The major difference between FCN based supervised learning and pix2pix based supervised learning is that the pix2pix framework extends an FCN model with an adversarial head as a discriminator to further improve the realism of the prediction. The major difference between the unsupervised framework and the self-supervised framework is that the unsupervised methods still require examples of the target images, even though the source images and target images do not need to be from the same sample or pixel-wise aligned. But, the self-supervised framework would only need the original images, which could be really helpful when it is impossible to acquire the target images (e.g., there is no truly noise-free or artifact-free image).

Currently, for supervised frameworks, both the FCN-type and pix2pix-type are well supported in the MMV\_Im2Im (RRID:SCR\_024630) package. Since our package is designed in a very generic way, it is possible to continuously expand the functionalities when available (ideally with community contributions). For example, diffusion models {[}\protect\hyperlink{ref-1A3yurr7m}{45}{]} can be thought of as a modern extension of the pix2pix-type framework and therefore are within our horizon to include into \emph{MMV\_Im2Im}. For the unsupervised framework, only CycleGAN-type methods are supported. We are planning to extend the unsupervised framework with Imaginaire (\url{https://github.com/NVlabs/imaginaire}), which will greatly extend the applicability of \emph{MMV\_Im2Im} (e.g., learning the transformation from one single image to another single image or one set of images to another set of images). Meanwhile, supporting the self-supervised framework will be our next major milestone.

@@

One of main directions for extending \emph{MMV\_Im2Im} is to pre-pack common bioimaging datasets as a Dataset module, so that DL researchers can use it for algorithm development and benchmarking, and new users can easily use it for learning microscopy image-to-image transformation. We will continue improving the functionalities of the package, such as supporting more models and methods, such as diffusion based models {[}\protect\hyperlink{ref-1A3yurr7m}{45}{]}, unsupervised denoising {[}\protect\hyperlink{ref-4vnyY9J9}{42}{]} or Imaginaire (\url{https://github.com/NVlabs/imaginaire}). Besides, we also plan to develop two auxiliary packages \emph{MMV\_Im2Im\_Auto} and \emph{MMV\_Im2Im\_Active}. In specific, when you have a reasonable amount of training data, \emph{MMV\_Im2Im\_Auto} will take advantage of the fact that MMV\_Im2Im is fully configurable with yaml files, and automatically generate a set of potentially good configurations, then find the optimal solution for you by cross validation. On the other hand, when you only have very limited training data, or even with only pseudo ground truth, \emph{MMV\_Im2Im\_Active} will help to build preliminary models from the limited training data, and gradually refine the model with human-in-the-loop by active learning {[}\protect\hyperlink{ref-jM3v1UjQ}{20}{]}. All the packages will also be wrapped into napari plugins {[}\protect\hyperlink{ref-YEMgt2T4}{46}{]} to allow no-code operation and therefore be more friendly to users without experience in programming.

The image-to-image transformation frameworks implemented in the current version do not explicitly take temporal information into account. We treat images (2D or 3D) at each time step independently. Thanks to the flexibility of aicsimageio, our package can directly read even multi-channel 3D timelapse data (i.e, 5D) during training or inference, if necessary. But the computation is done at individual time steps. A common method to integrate the temporal context with spatial information is the convolutional recurrent neural network (CRNN) {[}\protect\hyperlink{ref-s2RBSHdH}{47}{]}. The support of CRNN will be part of our future work.

Another type of microscopy image analysis problem related to image-to-image transformation is image registration, where we learn how to transform the ``floating'' image spatially so that it is optimally aligned with the reference image in the physical space. Recent methods are able to transform the floating image into its registered version through deep neural networks {[}\protect\hyperlink{ref-1Fh9QLxl9}{48}{]}. This will be another important direction for future extension.

@@

In general, all data used in this work were from open-accessible public repositories, released with other publications under open-source licenses. All data used in this work were only for research purposes, and we confirm that we didn't use these for any other non-commercial purpose or commercial purpose. The scripts we used to download and re-organize the data can be found in our release repository: https://github.com/MMV-Lab/mmv\_im2im/tree/main/paper\_configs/prepare\_data. Detailed information about each dataset is listed below, in the same order as the Results section.

@@

\textbf{2D:} The data were downloaded from \url{https://zenodo.org/record/6139958\#.Y78QJKrMLtU} and \url{https://zenodo.org/record/6140064\#.Y78YeqrMLtU}. We used all the data from the two sources, while 15\% of the data were held-out for testing. In specific, for data source 1 (\url{https://zenodo.org/record/6139958\#.Y78QJKrMLtU}), it contains a timelapse tiff of 240 time steps, each with 5 channels (only channel 3 and 5 were used in this work).

@@

For data source 2 (\url{https://zenodo.org/record/6140064\#.Y78YeqrMLtU}), it contains two sub-folders (train and test), each with snapshots sliced from different time lapse data. Each snapshot is saved as six different tiff files (only the \_bf and the second channel of \_fluo were used in this work):

@@

\leavevmode\vadjust pre{\hypertarget{ref-tuObtXMR}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{\textbf{DeStripe: A Self2Self Spatio-Spectral Graph Neural Network with~Unfolded Hessian for~Stripe Artifact Removal in~Light-Sheet Microscopy}
\CSLBlock{Yu Liu, Kurt Weiss, Nassir Navab, Carsten Marr, Jan Huisken, Tingying Peng} \emph{Lecture Notes in Computer Science} (2022) \url{https://doi.org/grxqnw}
\CSLBlock{DOI: \href{https://doi.org/10.1007/978-3-031-16440-8_10}{10.1007/978-3-031-16440-8\_10}}}

\leavevmode\vadjust pre{\hypertarget{ref-1A3yurr7m}{}}%
\CSLLeftMargin{45. }%
\CSLRightInline{\textbf{A Diffusion Model Predicts 3D Shapes from 2D Microscopy Images}
\CSLBlock{Dominik JE Waibel, Ernst Röell, Bastian Rieck, Raja Giryes, Carsten Marr} \emph{arXiv} (2022) \url{https://doi.org/gqrthn}
\CSLBlock{DOI: \href{https://doi.org/10.48550/arxiv.2208.14125}{10.48550/arxiv.2208.14125}}}

\leavevmode\vadjust pre{\hypertarget{ref-YEMgt2T4}{}}%
\CSLLeftMargin{46. }%
\CSLRightInline{\textbf{napari: a multi-dimensional image viewer for Python}
\CSLBlock{Jannis Ahlers, Daniel Althviz Moré, Oren Amsalem, Ashley Anderson, Grzegorz Bokota, Peter Boone, Jordão Bragantini, Genevieve Buckley, Alister Burt, Matthias Bussonnier, \ldots{} Kevin Yamauchi} \emph{Zenodo} (2023-07-05) \url{https://doi.org/gjpsxz}
\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.3555620}{10.5281/zenodo.3555620}}}

\leavevmode\vadjust pre{\hypertarget{ref-s2RBSHdH}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{\textbf{Self-Supervised Visual Feature Learning With Deep Neural Networks: A Survey}
\CSLBlock{Longlong Jing, Yingli Tian} \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence} (2021-11-01) \url{https://doi.org/gg8fm7}
\CSLBlock{DOI: \href{https://doi.org/10.1109/tpami.2020.2992393}{10.1109/tpami.2020.2992393}}}

\leavevmode\vadjust pre{\hypertarget{ref-1Fh9QLxl9}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{\textbf{Fast Symmetric Diffeomorphic Image Registration with Convolutional Neural Networks}
\CSLBlock{Tony CW Mok, Albert CS Chung} \emph{2020 IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)} (2020-06) \url{https://doi.org/gg99pz}
\CSLBlock{DOI: \href{https://doi.org/10.1109/cvpr42600.2020.00470}{10.1109/cvpr42600.2020.00470}}}

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/f4aeb90fb62535045c66cedb190c0d8e1c3373b7/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/f4aeb90fb62535045c66cedb190c0d8e1c3373b7}{MMV-Lab/im2im-paper@f4aeb90}
on December 12, 2023.

@@

Finally, we showed the comparison between three different types of models, an FCN-type model (i.e., fnet), a pix2pix-type model, and a CycleGAN-type model. For fair comparison, we used fnet as the same backbone for all three types of models. In theory, the pix2pix-type model can be trained in two different ways: from scratch or initializing the generator with a pre-trained fnet (trained as FCN). Examples of the comparison results were shown in the last two rows in Figure \ref{fig:labelfree_all_structures}-B. Visually, it is evident that the additional adversarial components (i.e., the discriminator) could generate images with more realistic appearance than a typical FCN-type model alone, but again, we leave the appropriate quantitative evaluations to users' specific biomedical studies.

@@

For 2D demonstration, we extracted the middle Z-slice from NPM1 images as the training target, while using the NPM1 segmentation results as the input binary masks. With the paired ``mask + microscopy image'' data, we could train the model in a supervised fashion, or randomly shuffle the data to simulate the situation without paired data which can be trained in an unsupervised fashion using the CycleGAN-type framework implemented in \emph{MMV\_Im2Im}. Example results can be found in Figure \ref{fig:synthetic}-A and Table \ref{tbl:syn}. In general, the supervised synthesization can generate more realistic images than the unsupervised model.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\caption{Overview of the used frameworks for the demonstrated tasks. \label{tbl:framework_overview}}\label{tbl:framework_overview}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Task
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dim
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Framework
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backbone
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Task
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dim
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Framework
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backbone
\end{minipage} \\
\midrule()
\endhead
Labelfree & 2D/3D & FCN, Pix2pix, CycleGAN & fnet, UNet, AttentionUnet, SwinUNETR, \ldots{} \\
Semantic segmentation & 2D/3D & FCN, CycleGAN & AttentionUnet, DynUnet, UNet3D \\
Instance segmentation & 2D/3D & EmbedSeg & BranchedERFNet\_2d, UNet3D \\
Synthetic & 2D/3D & Pix2pix & AttentionUnet, fnet \\
Denoising & 3D & FCN & UNet \\
Modality transformation & 3D & FCN & UNet3D \\
Staining transformation & 2D & Pix2pix & predefined\_unet \\
\bottomrule()
\end{longtable}

@@

Overall, the package inherited the boilerplate concept from pytorch-lightning {[}\protect\hyperlink{ref-YbvSvdyB}{14}{]}, and was made fully configurable via yaml files supported by pyrallis {[}\protect\hyperlink{ref-17WhsEZko}{44}{]}, as well as largely employed state-of-the-art DL components from MONAI {[}\protect\hyperlink{ref-UU62HYC6}{18}{]}. The three key parts in the package: \texttt{mmv\_im2im.models}, \texttt{mmv\_im2im.data\_modules}, and \texttt{Trainers}, will be further described below.

@@

In general, there are mainly four major DL frameworks that could be applied to microscopy image-to-image transformation: supervised learning with a fully convolutional networks (FCN) type models, supervised learning with pix2pix type models, unsupervised learning to learn mapping between visual domains, and Self2Self-type self-supervised learning {[}\protect\hyperlink{ref-tuObtXMR}{45}{]}. The major difference between FCN based supervised learning and pix2pix based supervised learning is that the pix2pix framework extends an FCN model with an adversarial head as a discriminator to further improve the realism of the prediction. The major difference between the unsupervised framework and the self-supervised framework is that the unsupervised methods still require examples of the target images, even though the source images and target images do not need to be from the same sample or pixel-wise aligned. But, the self-supervised framework would only need the original images, which could be really helpful when it is impossible to acquire the target images (e.g., there is no truly noise-free or artifact-free image).

Currently, for supervised frameworks, both the FCN-type and pix2pix-type are well supported in the MMV\_Im2Im (RRID:SCR\_024630) package. Since our package is designed in a very generic way, it is possible to continuously expand the functionalities when available (ideally with community contributions). For example, diffusion models {[}\protect\hyperlink{ref-1A3yurr7m}{46}{]} can be thought of as a modern extension of the pix2pix-type framework and therefore are within our horizon to include into \emph{MMV\_Im2Im}. For the unsupervised framework, only CycleGAN-type methods are supported. We are planning to extend the unsupervised framework with Imaginaire {[}\protect\hyperlink{ref-vzOBQiEH}{47}{]}, which will greatly extend the applicability of \emph{MMV\_Im2Im} (e.g., learning the transformation from one single image to another single image or one set of images to another set of images). Meanwhile, supporting the self-supervised framework will be our next major milestone.

@@

One of main directions for extending \emph{MMV\_Im2Im} is to pre-pack common bioimaging datasets as a Dataset module, so that DL researchers can use it for algorithm development and benchmarking, and new users can easily use it for learning microscopy image-to-image transformation. We will continue improving the functionalities of the package, such as supporting more models and methods, such as diffusion based models {[}\protect\hyperlink{ref-1A3yurr7m}{46}{]}, unsupervised denoising {[}\protect\hyperlink{ref-4vnyY9J9}{42}{]} or Imaginaire (\url{https://github.com/NVlabs/imaginaire}). Besides, we also plan to develop two auxiliary packages \emph{MMV\_Im2Im\_Auto} and \emph{MMV\_Im2Im\_Active}. In specific, when you have a reasonable amount of training data, \emph{MMV\_Im2Im\_Auto} will take advantage of the fact that MMV\_Im2Im is fully configurable with yaml files, and automatically generate a set of potentially good configurations, then find the optimal solution for you by cross validation. On the other hand, when you only have very limited training data, or even with only pseudo ground truth, \emph{MMV\_Im2Im\_Active} will help to build preliminary models from the limited training data, and gradually refine the model with human-in-the-loop by active learning {[}\protect\hyperlink{ref-jM3v1UjQ}{20}{]}. All the packages will also be wrapped into napari plugins {[}\protect\hyperlink{ref-YEMgt2T4}{48}{]} to allow no-code operation and therefore be more friendly to users without experience in programming.

The image-to-image transformation frameworks implemented in the current version do not explicitly take temporal information into account. We treat images (2D or 3D) at each time step independently. Thanks to the flexibility of aicsimageio, our package can directly read even multi-channel 3D timelapse data (i.e, 5D) during training or inference, if necessary. But the computation is done at individual time steps. A common method to integrate the temporal context with spatial information is the convolutional recurrent neural network (CRNN) {[}\protect\hyperlink{ref-s2RBSHdH}{49}{]}. The support of CRNN will be part of our future work.

Another type of microscopy image analysis problem related to image-to-image transformation is image registration, where we learn how to transform the ``floating'' image spatially so that it is optimally aligned with the reference image in the physical space. Recent methods are able to transform the floating image into its registered version through deep neural networks {[}\protect\hyperlink{ref-1Fh9QLxl9}{50}{]}. This will be another important direction for future extension.

@@

In general, all data used in this work were from open-accessible public repositories, released with other publications under open-source licenses. All data used in this work were only for research purposes, and we confirm that we didn't use these for any other non-commercial purpose or commercial purpose. The scripts we used to download and re-organize the data can be found in our release repository: https://github.com/MMV-Lab/mmv\_im2im/tree/main/paper\_configs/prepare\_data. Detailed information about each dataset is listed below, in the same order as the Results section. Snapshots of our code and other data further supporting this work are openly available in the GigaScience repository, GigaDB {[}xx\#\#{]}. In addition, we uploaded all the trained models and sample data to a Zenodo bucket {[}\protect\hyperlink{ref-FBoj3fXM}{51}{]} to ensure the reproducibility of our work.

@@

\textbf{2D:} The data were downloaded from {[}\protect\hyperlink{ref-xv2VIyRP}{25}{]} and {[}\protect\hyperlink{ref-8ywSgqrJ}{52}{]}. We used all the data from the two sources, while 15\% of the data were held-out for testing. In specific, for data source 1 (\url{https://zenodo.org/record/6139958\#.Y78QJKrMLtU}), it contains a timelapse tiff of 240 time steps, each with 5 channels (only channel 3 and 5 were used in this work).

@@

For data source 2 {[}\protect\hyperlink{ref-8ywSgqrJ}{52}{]}, it contains two sub-folders (train and test), each with snapshots sliced from different time lapse data. Each snapshot is saved as six different tiff files (only the \_bf and the second channel of \_fluo were used in this work):

@@

\leavevmode\vadjust pre{\hypertarget{ref-17WhsEZko}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{\textbf{Pyrallis - Simple Configuration with Dataclasses}
\CSLBlock{Elad Richardson, Ido Weiss, Yair Feldman} \emph{Github} \url{https://github.com/eladrich/pyrallis}}

\leavevmode\vadjust pre{\hypertarget{ref-tuObtXMR}{}}%
\CSLLeftMargin{45. }%
\CSLRightInline{\textbf{DeStripe: A Self2Self Spatio-Spectral Graph Neural Network with~Unfolded Hessian for~Stripe Artifact Removal in~Light-Sheet Microscopy}
\CSLBlock{Yu Liu, Kurt Weiss, Nassir Navab, Carsten Marr, Jan Huisken, Tingying Peng} \emph{Lecture Notes in Computer Science} (2022) \url{https://doi.org/grxqnw}
\CSLBlock{DOI: \href{https://doi.org/10.1007/978-3-031-16440-8_10}{10.1007/978-3-031-16440-8\_10}}}

\leavevmode\vadjust pre{\hypertarget{ref-1A3yurr7m}{}}%
\CSLLeftMargin{46. }%
\CSLRightInline{\textbf{A Diffusion Model Predicts 3D Shapes from 2D Microscopy Images}
\CSLBlock{Dominik JE Waibel, Ernst Röell, Bastian Rieck, Raja Giryes, Carsten Marr} \emph{arXiv} (2022) \url{https://doi.org/gqrthn}
\CSLBlock{DOI: \href{https://doi.org/10.48550/arxiv.2208.14125}{10.48550/arxiv.2208.14125}}}

\leavevmode\vadjust pre{\hypertarget{ref-vzOBQiEH}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{\textbf{Imaginaire}
\CSLBlock{Imaginaire Contributors} \emph{Github} \url{https://github.com/NVlabs/imaginaire}}

\leavevmode\vadjust pre{\hypertarget{ref-YEMgt2T4}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{\textbf{napari: a multi-dimensional image viewer for Python}
\CSLBlock{Jannis Ahlers, Daniel Althviz Moré, Oren Amsalem, Ashley Anderson, Grzegorz Bokota, Peter Boone, Jordão Bragantini, Genevieve Buckley, Alister Burt, Matthias Bussonnier, \ldots{} Kevin Yamauchi} \emph{Zenodo} (2023-07-05) \url{https://doi.org/gjpsxz}
\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.3555620}{10.5281/zenodo.3555620}}}

\leavevmode\vadjust pre{\hypertarget{ref-s2RBSHdH}{}}%
\CSLLeftMargin{49. }%
\CSLRightInline{\textbf{Self-Supervised Visual Feature Learning With Deep Neural Networks: A Survey}
\CSLBlock{Longlong Jing, Yingli Tian} \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence} (2021-11-01) \url{https://doi.org/gg8fm7}
\CSLBlock{DOI: \href{https://doi.org/10.1109/tpami.2020.2992393}{10.1109/tpami.2020.2992393}}}

\leavevmode\vadjust pre{\hypertarget{ref-1Fh9QLxl9}{}}%
\CSLLeftMargin{50. }%
\CSLRightInline{\textbf{Fast Symmetric Diffeomorphic Image Registration with Convolutional Neural Networks}
\CSLBlock{Tony CW Mok, Albert CS Chung} \emph{2020 IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)} (2020-06) \url{https://doi.org/gg99pz}
\CSLBlock{DOI: \href{https://doi.org/10.1109/cvpr42600.2020.00470}{10.1109/cvpr42600.2020.00470}}}

\leavevmode\vadjust pre{\hypertarget{ref-FBoj3fXM}{}}%
\CSLLeftMargin{51. }%
\CSLRightInline{\textbf{MMV\_Im2Im: An Open Source Microscopy Machine Vision Toolbox for Image-to-Image Transformation}
\CSLBlock{Justin Sonneck, Yu Zhou, Jianxu Chen} \emph{Zenodo} (2023-10-24) \url{https://doi.org/gs8p4r}
\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.10034416}{10.5281/zenodo.10034416}}}

\leavevmode\vadjust pre{\hypertarget{ref-8ywSgqrJ}{}}%
\CSLLeftMargin{52. }%
\CSLRightInline{\textbf{Automatic labelling of HeLa "Kyoto" cells using Deep Learning tools}
\CSLBlock{Romain Guiet} \emph{Zenodo} (2022-02-25) \url{https://doi.org/gs8p4s}
\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.6140063}{10.5281/zenodo.6140063}}}
